Finding Quality Issues in SKOS Vocabularies

### 2012-03-27 introduction.tex
read and fixed 1-3

% What is SKOS?
The Simple Knowledge Organization System (SKOS)~\cite{Miles2005} is a standard model for sharing and linking controlled vocabularies on the Web. Many organizations, including the European Union\footnote{EuroVoc, \url{http://eurovoc.europa.eu/}}, the United Nations\footnote{AGROVOC, \url{http://aims.fao.org/website/AGROVOC-Thesaurus/sub}}, or the UK government\footnote{Integrated Public Sector Vocabulary (IPSV), \url{http://doc.esd.org.uk/IPSV}} published SKOS representations of their controlled vocabularies on the Web so that they can easily be accessed and by humans and machines.

% What does "quality" mean in this context?
Each vocabulary reflects domain- and application-specific needs and taxonomists often follow existing standards \cite{ISO25964-1:2011,Z39.19:2005} or apply their own hand-crafted checks (cf.,~\cite{Coronado2009}) to meet certain quality requirements. However, these requirements can differ across domains and lead to quality problems when a vocabulary is used in other environments. As a consequence, currently available vocabularies are, even though they are expressed in SKOS, often heterogeneous in terms of quality. The following examples illustrate that this can affect their applicability for tasks like query expansion, faceted browsing, clustering, or auto-completion:

@@

	\item The SKOS representation of AGROVOC defines concepts in 25 different languages. However, while most concepts have an English description, only 38\% of all concepts have German labels attached. This can be a problem for applications that use Agrovoc and rely on German translations.

	\item An earlier version (v.8.06) of the STW thesaurus contained 5 pairs of concepts with identical labels. As a result, the auto-complete function of the online search interface at that time suggested identical entries, without giving disambiguation information.

% Note: examples related to "defense / army & co" are always a bit tricky; maybe we find a better example.

@@

The SKOS specification doesn't make any explicit statements about vocabulary quality. It defines a set of \textbf{integrity conditions} that state ``whether or not given data are consistent with respect to the SKOS data model''~\cite{Miles2005}. Existing quality checking tools, such as the PoolParty Thesaurus Consistency Checker\footnote{\url{http://demo.semantic-web.at:8080/SkosServices/check}} or SKOSify\footnote{\url{http://code.google.com/p/skosify/}} can be used to verify that a given vocabulary fulfills these conditions. However, these conditions fail to capture quality aspects such as those mentioned in the examples before, aspects that go beyond integrity conditions of the SKOS data model. Existing guidelines and manuals consider these aspects but currently rely on \textbf{human judgement}, which is subjective and does not scale for larger, possibly linked vocabularies on the Web.

@@

	\item With the \textbf{qSKOS quality assessment tool} we provide a reference implementation of these filtering functions.

	\item We \textbf{analyzed} a representative set of 15 \textbf{existing SKOS vocabularies} to learn about possible quality issues in existing Web vocabularies.

@@

In the following, we will first discuss what \emph{quality} means in the context of SKOS vocabularies and how it is currently support by the SKOS specification and existing tools. Then we introduce the quality issues we have identified and describe how we implemented them in the qSKOS quality assessment tool. Finally, we report on the results of an analysis we performed on 15 existing SKOS vocabularies and which shows that the quality issues we identified occur in reality. The reports we produced already lead to the improvement of at least two existing vocabularies.

>>>>

% What is SKOS?
The Simple Knowledge Organization System (SKOS)~\cite{Miles2005} is a standard model for sharing and linking controlled vocabularies on the Web. Many organizations, including the European Union\footnote{EuroVoc, \url{http://eurovoc.europa.eu/}}, the United Nations\footnote{AGROVOC, \url{http://aims.fao.org/website/AGROVOC-Thesaurus/sub}}, or the UK government\footnote{Integrated Public Sector Vocabulary (IPSV), \url{http://doc.esd.org.uk/IPSV}} publish SKOS representations of their controlled vocabularies on the Web so that they can easily be accessed by humans and machines.

% What does "quality" mean in this context?
Each vocabulary reflects domain- and application-specific needs and taxonomists often follow existing standards (cf.,~\cite{ISO25964-1:2011,Z39.19:2005}) or apply their own hand-crafted checks (cf.,~\cite{Coronado2009}) to meet certain quality requirements. However, quality requirements can differ across application domains. The following examples illustrate how quality issues can affect the applicability of SKOS vocabularies for tasks such as query expansion, faceted browsing, or auto-completion:

@@

	\item The SKOS representation of AGROVOC defines concepts in 25 different languages. However, while most concepts have an English description, only 38\% have German labels attached. This can be a problem for multilingual applications that rely on label translations.

	\item An earlier version (v.8.06) of the STW thesaurus contained 5 pairs of concepts with identical labels. As a result, the auto-complete function of the online search interface suggested identical entries, without giving disambiguation information.

% Note: can we replace the LvAK with an example from a public vocabulary? Then we could simply exclude that vocabulary from that paper.

@@

The SKOS specification doesn't make any explicit statements about vocabulary quality. It defines a set of \textbf{integrity conditions} that state ``whether or not given data are consistent with respect to the SKOS data model''~\cite{Miles2005}. Existing quality checking tools, such as the PoolParty Thesaurus Consistency Checker\footnote{\url{http://demo.semantic-web.at:8080/SkosServices/check}} or SKOSify\footnote{\url{http://code.google.com/p/skosify/}} can be used to validate vocabularies against these conditions. However, these conditions fail to capture quality aspects such as those mentioned in the examples before, aspects that go beyond integrity conditions of the SKOS data model. Existing guidelines and manuals consider these aspects but currently rely on \textbf{human judgement}, which is subjective and does not scale for larger, possibly linked vocabularies on the Web.

@@

	\item With the \textbf{qSKOS quality assessment tool} we provide a reference implementation of these functions.

	\item We \textbf{analyzed} a representative set of \textbf{15 existing SKOS vocabularies} to learn about possible quality issues in existing Web vocabularies.

@@

In the following, we will first discuss what \emph{quality} means in the context of SKOS vocabularies and how it is currently support by the SKOS specification and existing tools. Then we introduce the quality issues we have identified and describe how we implemented them in the qSKOS quality assessment tool. Finally, we report on the results of an analysis we performed on 15 existing SKOS vocabularies and which shows that the quality issues we discussed are real and can lead to the improvement of existing vocabularies.

### 2012-03-27 main.tex
updated intro
fixed first table
read and fixed 1-3

@@

\title{Quality Criteria for SKOS Vocabularies}
\author{Christian Mader\inst{1} \and Bernhard Haslhofer\inst{2}}
\institute{
	University of Vienna, Faculty of Computer Science\\\email{christian.mader@univie.ac.at}
	\and Cornell University, Information Science\\\email{bernhard.haslhofer@cornell.edu}}

@@

The Simple Knowledge Organization System (SKOS) has become a standard model for controlled vocabularies on the Web. However, SKOS vocabularies often differ in terms of quality, which reduces their applicability across system boundaries. Here we investigate how we can support taxonomists in improving the quality of SKOS vocabularies by pointing out quality issues that go beyond the integrity constraints defined in the SKOS specification. We identified possible \textbf{quality issues} and formalized them into computable \textbf{quality checking functions} that can find affected resources in a given SKOS vocabulary. We implemented these functions in the qSKOS quality assessment tool, analyzed 15 existing vocabularies, and found possible quality issues in all of them.

@@

>>>>

\usepackage{array}

@@

\title{Finding Quality Issues in SKOS Vocabularies}
\author{Christian Mader\inst{1} \and Bernhard Haslhofer\inst{2}}
\institute{
	University of Vienna, Faculty of Computer Science\\\email{christian.mader@univie.ac.at}
	\and Cornell University, Information Science\\\email{bernhard.haslhofer@cornell.edu}}

@@

The Simple Knowledge Organization System (SKOS) has become a standard model for controlled vocabularies on the Web. However, SKOS vocabularies often differ in terms of quality, which reduces their applicability across system boundaries. Here we investigate how we can support taxonomists in improving SKOS vocabularies by pointing out quality issues that go beyond the integrity constraints defined in the SKOS specification. We identified potential \textbf{quality issues} and formalized them into computable \textbf{quality checking functions} that can find affected resources in a given SKOS vocabulary. We implemented these functions in the qSKOS quality assessment tool, analyzed 15 existing vocabularies, and found possible quality issues in all of them.

@@

% \section{Acknowledgements}

% Tom Dent (esd support team) for providing a dump for the IPSV vocabulary
% Andrew Gibson for providing a dump for the Peroxisome knowledge Base and giving valuable feedback on their vocabulary structure.
